Grove: A Convergent Collaborative Structure-Editor Calculus

### 2020-12-03 grove-paper.tex
Revisions to "Cycle" section

\figureSimple

@@

\figureWrap

@@

\figureMove

@@

\figureDifferentParts

%\figureCommutativity
\begin{figure}
  \centering
  \begin{tikzpicture}
    \path (-3cm, 0cm) node (a) [align=center]            {Original \\ Version};
    \path ( 0cm, 1cm) node (b) [align=center,alice node] {Alice's  \\ Version};
    \path ( 0cm,-1cm) node (c) [align=center,bob node]   {Bob's    \\ Version};
    \path ( 3cm, 0cm) node (d) [align=center]            {Synchronized \\ Version};
    \path [draw,->,alice step] (a) -- node [pos=0.7,align=center,auto]      {Alice's \\ Edits} (b);
    \path [draw,->,bob step]   (a) -- node [pos=0.7,align=center,auto,swap] {Bob's \\ Edits}   (c);
    \path [draw,->,merge step] (b) -- node [pos=0.3,align=center,auto]      {Share \\ Edits} (d);
    \path [draw,->,merge step] (c) -- node [pos=0.3,align=center,auto,swap] {Share \\ Edits} (d);
  \end{tikzpicture}
  \caption{Commutativity of Edits.}
  \label{fig:Commutativity}
\end{figure}

@@

\figureNestedParts

@@

\figureMultiChild

@@

\figureMultiParent

@@

% \figureSingleUserCycles

@@

\figureCycle

TODO: technically a multi-parent conflict

TODO: paragraph about why single-user cycles cannot happen.
While single-user edits can be checked to see
whether they create a cycle and thus the system
can immediately warn the user,
multi-user edits may not manifest cycles until after
the edits from multiple users are merged.

@@

On their own, neither of these edits creates a cycle.
However, merging the edit actions of both Alice and Bob results in the graph
in \autoref{fig:Cycle:d}, which has a cycle
between~\vMultiCycleTimes{} and~\vMultiCyclePlus{}.
As with the other kinds of conflict, resolving it requires user input, but is as simple as
either deleting~\eMultiCycleBobPlus{} and~\eMultiCycleBobTimes{}~(thus favoring Alice's version)
or deleting~\eMultiCycleAliceTimes{} and~\eMultiCycleAlicePlus{}~(thus favoring Bob's version).
Since a cycle like this that is connected to the root vertex always
contains vertexes with multiple parents that if removed would break the cycle,
we use the user interface described in \autoref{sub:Multi-parent conflicts}
to display these kinds of programs.
For example, \autoref{fig:Cycle:d} would be displayed.
We leave the user interface considerations of resolving the conflict such a
cycle represents to future work.

@@

\figureDisconnect

@@

>>>>

\figureSimple{}

@@

\figureWrap{}

@@

\figureMove{}

@@

\figureDifferentParts{}

%\figureCommutativity{}
\begin{figure}
  \centering
  \begin{tikzpicture}
    \path (-3cm, 0cm) node (a) [align=center]            {Original \\ Version};
    \path ( 0cm, 1cm) node (b) [align=center,alice node] {Alice's  \\ Version};
    \path ( 0cm,-1cm) node (c) [align=center,bob node]   {Bob's    \\ Version};
    \path ( 3cm, 0cm) node (d) [align=center]            {Synchronized \\ Version};
    \path [draw,->,alice step] (a) -- node [pos=0.7,align=center,auto]      {Alice's \\ Edits} (b);
    \path [draw,->,bob step]   (a) -- node [pos=0.7,align=center,auto,swap] {Bob's \\ Edits}   (c);
    \path [draw,->,merge step] (b) -- node [pos=0.3,align=center,auto]      {Share \\ Edits} (d);
    \path [draw,->,merge step] (c) -- node [pos=0.3,align=center,auto,swap] {Share \\ Edits} (d);
  \end{tikzpicture}
  \caption{Commutativity of Edits.}
  \label{fig:Commutativity}
\end{figure}

@@

\figureNestedParts{}

@@

\figureMultiChild{}

@@

\figureMultiParent{}

@@

% \figureSingleUserCycles{}

@@

\figureCycle{}

@@

On their own, neither of these edits creates a cycle.
However, merging the edit actions of both Alice and Bob results in the graph
in \autoref{fig:Cycle:d}, which has a cycle
between~\vMultiCycleTimes{} and~\vMultiCyclePlus{}.
As with the other kinds of conflict, resolving it requires user input.
For example, by either deleting both~\eMultiCycleBobPlus{} and~\eMultiCycleBobTimes{}~(thus favoring Alice's version)
or deleting both~\eMultiCycleAliceTimes{} and~\eMultiCycleAlicePlus{}~(thus favoring Bob's version).

@@

\figureDisconnect{}

@@

Finally, there is a particular type of cycle worth discussing.

Since a cycle like this that is connected to the root vertex always
contains vertexes with multiple parents that if removed would break the cycle,
we use the user interface described in \autoref{sub:Multi-parent conflicts}
to display these kinds of programs.
For example, \autoref{fig:Cycle:d} would be displayed.
We leave the user interface considerations of resolving the conflict such a
cycle represents to future work.
